---
title: "Brownlows Bets"
author: "Mariah Kee"
date: "November 12, 2020"
output: 
  html_document:
    number_sections: true
    toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(tidyverse)
require(tigerstats)
require(knitr)
```
### `r as.character(Sys.Date())`



<!-- We recommend you use git branches -- create a separate branch for each major section i.e. Introduction, Methods, Results, Inferential Results, and Discussion and Conclusions - leave the YAML block untouched until the final merge where you put in your own name !-->

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->

 At the first day of class there are 35 students in Math Statistics class and professor Brownlow always proposes this bet to his students "I will wager $2 to your bet of $1 that at least two people in today's class have  the same birthday.  He tells me he has made that bet 637 times so far. Where do you think his profits are? Discuss this in a markdown document

# Methods

<!--Decide on your methods:  In this section explain the approach you will take to attack the issue --- how will you decide on a likely estimate of professor Brownlow's earnings or losses after 637 bets. Also explain how you construct a 95% confidence interval about your estimate of his winnings !-->
We will solve this problem by resampling, we will set up days of the year, take a random sample of 35 and see if two or more have the same birthday.    
```{r}
daysYEAR=1:365
bDAYS=sample(daysYEAR,35,replace=TRUE)
length(unique(bDAYS))
```

```{r}
bank=0
for(i in 1:365){
    class=sample(daysYEAR,35,replace=TRUE)
n=length(unique(class))
if(n== 35)bank=bank-2
else bank =bank+1
}
print(bank)
```

```{r}
results=vector("numeric")
for(j in 1:1000){
bank=0
for(i in 1:637){
    class= sample(daysYEAR,35,replace=TRUE) 
     n=length(unique(class))
     if(n == 35)bank=bank-2
     else bank=bank+1
}
results[j]=bank
}
hist(results)
```


# Profit Estimate




```{r}
favstats(results)
```
the expected amount of money is `r mean(results)`

<!--Explain and display the results of your method of coming up with the estimate of professor Brownlows betting profits!-->
# Confidence interval of Brownlows earning   
#95% confidence interval   
```{r}
results=vector("numeric")
for(j in 1:1000){
bank=0
for(i in 1:637){
    class= sample(daysYEAR,35,replace=TRUE) 
     n=length(unique(class))
     if(n == 35)bank=bank-2
     else bank=bank+1
}
results[j]=bank
}
sortRESULTS=sort(results)
lcl=sortRESULTS[25]
ucl=sortRESULTS[975]

```
lower confidence limit= `r lcl`    
upper confidence limit= `r lcl`    



#fair odds payoff  
```{r}
results=vector("numeric")
for(j in 1:1000){
bank=0
for(i in 1:637){
    class= sample(daysYEAR,35,replace=TRUE) 
     n=length(unique(class))
     if(n == 35)bank=bank-4.5
     else bank=bank+1
}
results[j]=bank
}
hist(results)
```
the amount that dr j would have to pay to make this a fair bet is 4.5   

#number of students for a fair bet   

```{r}
results=vector("numeric")
for(j in 1:1000){
bank=0
for(i in 1:637){
    class= sample(daysYEAR,29,replace=TRUE) 
     n=length(unique(class))
     if(n == 29)bank=bank-2
     else bank=bank+1
}
results[j]=bank
}
hist(results)
```
   
# Discussion and Conclusion
<!--Discussion and conclusion here.  If professor Brownlow is consistantly making or losing money how could he change his payout so that his profits center on zero?  Also discuss what size his class should be in order to have his current scheme balance at zero profit.!-->

We have determined that in order for this to be a fair bet we need 29 students in the class and dr j has to bet $450 in order for it to be a fair bet. The answers couldbe infinate depending on the class size, the bigger the class size the more likely he is to win.     

